### 2019-09-06 manuscript/figures.Rmd
fix diagnositic table labeling

```{r 03_model_summary, results='asis', warning=FALSE, echo = FALSE}
knitr::kable('\\includegraphics{"../tables/03_model_summary"}', col.names = NULL, caption = "Model selection diagnostics")
```

>>>>

```{r 03_model_summary, results='asis', warning=FALSE, echo = FALSE}
knitr::kable('\\includegraphics[width=5in]{"../tables/03_model_summary"}', col.names = NULL, caption = "Model selection diagnostics")
```

### 2019-09-06 tables/03_model_summary.Rmd
fix diagnositic table labeling

options(knitr.kable.NA = "-")  
dt %>%
  # dplyr::filter(str_detect(response, "tp")) %>%
  # dplyr::select(-response) %>%
  dplyr::rename("$R^2$" = r2) %>%
  knitr::kable(digits = 2, format = "markdown", caption = "TP Model R2")
```

>>>>

options(knitr.kable.NA = "-")  
dt %>%
  # dplyr::filter(str_detect(response, "tp")) %>%
  # dplyr::select(-response) %>%
  dplyr::rename("$R^2$" = r2, 
                "LOO-ELPD" = elpd_diff) %>%
  knitr::kable(digits = 2, format = "markdown", caption = "TP Model R2", 
               row.names = FALSE)
```
